### 2016-03-13 paper/result_stereo.tex
hang

We performed our experiments on the half-size Book sequence from Middlebury stereo
datasets.~\cite{middlebury_stereo}. We use 7 images with the
resolution of $695\times555$ and optimize for 256 disparity labels. We
recoreded both single thread energy and system energy (minimum energy
so far from all threads) against time.

>>>>

We performed our experiments on the Book sequence from Middlebury stereo
datasets.~\cite{middlebury_stereo}. We use 7 images with the
resolution of $695\times555$ and optimize for 256 disparity labels. We
recoreded both single thread energy and system energy (minimum energy
so far from all threads) against time. Since the order of labels to be
expanded or fused will have impact on minimization, we randomly
shuffled 256 labels and provide this order to all methods.

### 2016-03-13 paper/results.tex
hang

\section{Experimental results}
\label{section:results}
We have implemented the algorithms in C++ and conducted the experiments
on Linux PCs with Intel Core i7 processor with 4 cores, enabling 8 threads
with the hyper threading technology. We have used the Graph-cuts
optimization code written by Veksler, using the libraries provided by
Boykov and Kolmogorov~\cite{middle_bury,2,3,4_below}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{msr_link?,trw_link}.

>>>>

\section{Experimental results}
\label{section:results}
We have implemented the algorithms with multithreading supporting from
C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
4790 processor with 4 cores, enabling 8 threads with the hyper
threading technology. We have used the Graph-cuts optimization code
written by Veksler, using the libraries provided by Boykov and
Kolmogorov~\cite{middle_bury,2,3,4_below}.
% [2] Fast Approximate Energy Minimization via Graph Cuts.
%         Y. Boykov, O. Veksler, and R. Zabih.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
%
%     [3] What Energy Functions can be Minimized via Graph Cuts?
%         V. Kolmogorov and R. Zabih. 
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
%         An earlier version appeared in European Conference on Computer
%         Vision (ECCV), May 2002.
%
%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
%         Energy Minimization in Vision. 
%         Y. Boykov and Vladimir Kolmogorov.
%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
We have used the QPBO and TRW-S implementations by
Kolmogorov~\cite{msr_link?,trw_link}.

\input{result_stereo}
